An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$

### 2019-12-31 paper.tex
Rewrite IOTA PoW explanation

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
	\item	Tips selection: In IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
	\item	Proof-of-Work (PoW): Perform a series of mathametic calculation for the transaction in order to be validated.
\end{itemize}

>>>>

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
	\item	Tips selection: In IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes.
	\item	Proof-of-Work (PoW): An algorithm which prevents Denial of Service and spam attacks on a network. a computationally hard puzzle to solve, but easy to verify. IOTA uses a Hashcash\cite{Hashcash} based puzzle.
\end{itemize}
